\chapter{Graphic Design}

\bence{- 5: illetve érdemes lenne előbb az implementálandó feature-ökről, azok prioritásairól írni, majd ezután továbbmenni arra, hogy mi a fontos ezekből az UI-n.  Ha ez megvan, akkor lehet kitérni arra, hogy ezt 	hogyan képzeled el a felületen.}

\bence{- 4 és 5 között hiányzik számomra az a rész, ahol az implementáció \_előtt\_ lefekteted azokat a kritériumokat, amik alapján "elfogadott" (elfogadható) lesz a kezedből kiadott eredmény -- és amit a 6/7. fejezetben tesztelsz.}

\section{Design Sketches}
To be able to draw design sketches, we need to know when will a user login to the Educational Support System and what kind of informations is he looking for. As a student, there are 5 possible scenarios:

\begin{enumerate}
	\item Before a laboratory
	\begin{itemize}
		\item To get informations about the laboratory
		\begin{itemize}
			\item When will it be
			\item Where will it be
			\item Who will be the teacher
		\end{itemize}
		\item To read general informations about the course
	\end{itemize}
	
	\item During a laboratory
	\begin{itemize}
		\item To upload an SSH public key
		\item To get his Git remote URL
	\end{itemize}
	
	\item After a laboratory, before deadline
	\begin{itemize}
		\item To see the date of the deadline
		\item To see how much time is left until the deadline
		\item To see the pushed branches, commits and tags
		\item To tag a commit as final version
	\end{itemize}
	
	\item After a laboratory, after deadline
	\begin{itemize}
		\item To check his grades
		\item To check his reviews
		\item To check the evaluator's name
	\end{itemize}
	
	\item Other scenarios
	\begin{itemize}
		\item To set a new e-mail address
		\item To change his mailing list subscription
		\item To change his e-mail notification subscription
		\item To see a summarized table of his grades
	\end{itemize}
	
\end{enumerate}

With the scenarios and list of actions, we can see how many pages is needed for the student modules and how many states will one page have. I drew sketches \see{appendix-design-sketches} for every state with placeholder data. Because the user is looking for a specific set of information, the page will only contain that he is looking for, and the previous, but still relevant informations will be accessible via submenus. Other pages, e.g., other laboratories, settings and summary, will be accessible via a menu.

\section{Design template}

To show only a specific set of information I have decided to use a minimalist design. A minimalist design is a clear design, focusing on typography, space, color and basic design elements. This way the portal will show as much information as the user needs with as few elements as possible. 

To look for templates and ideas I read the Designmodo blog~\cite{Designmodo} and checked all the popular websites, e.g., Facebook, Github, Twitter and Medium. Designmodo also have purchasable website builders, like Slides~\cite{Designmodo-slides}, but I prefer the simple design of the Bootstrap elements~\cite{Bootstrap}. 

Bootstrap is a free and open source HTML, CSS and JS framework to create responsive design. It was originally a part of Twitter as Twitter Blueprint, but in 2011 it was released as an open source project. Bootstrap contains elements for responsive web design and mobile design. Bootstrap 4 alpha was launched in August 2015 alongside with a new side project, Official Bootstrap Themes~\cite{Bootstrap-themes}. Bootstrap Themes are purchasable redesigned collections of Bootstrap components with new components and plugins. Although I really like these themes, I will use the free components, because it does not worth buying any theme if I will change some parts of the included components. 

\subsection{Colors}0

After deciding what kind of design framework will I use, I had to chose the colors of the portal. Both the Budapest University of Technology and Economics~\cite{BME-Arculat}~\cite{BME-Arculat-Intranet} and the Faculty of Electrical Engineering and Informatics~\cite{VIK-Arculat}~\cite{VIK-Arculat-PDF} have their own Visual Identity Guidelines. A visual identity guideline contains the description of which color is the official color of the institution and in what kind of text which fonts and why that font should be used.

I consulted with my advisor, Sándor Gajdos and he told me that I should not follow any of the visual identity guidelines. Following any of the strict guidelines can be a problem in the future, if anyone would like to use this portal for another course that does not belong to the faculty or the university. Based on a subjective opinion I have decided to use green as the main color of the portal. I have used the Google Color palette~\cite{google-color-chart} to choose a nice green, changed it a bit, and I got the final color, \#2a623d.

\section{Elkészítés módszere}

html, js, css, bootstrap css

\todo{elkészítés módszere}

\section{Rendszer kinézete}

screenshotok

\todo{hogy néz ki a rendszer}